---
title: "Customer Segmentation"
author: "Akash Lamba"
output: 
      github_document:
          toc: TRUE
---
### Overview
* You are owning a supermarket mall and through membership cards. 
* You have some basic data about your customers like :
      + Customer ID
      + age
      + gender 
      + annual income  
      + spending score
* Spending Score is something you assign to the customer based on your defined parameters like customer        behavior and purchasing data.
* In our Dataset the spending score is between 1 to 100 for each customer.

### Problem Statement
You own the mall and want to understand the customers like who can be easily converge [Target Customers] so that the sense can be given to marketing team and plan the strategy accordingly.


### Loading Packages
```{r,warning=FALSE,message=FALSE}
library(cluster)
```

### Importing the data
```{r}
customers = read.csv('Mall_Customers.csv')
```


### Structure
```{r}
str(customers)
```
*We have 200 observations and 5 variables in our dataset.*

### Data Glimpse
```{r}
head(customers)
customers<-customers[4:5]
```
*We are subsetting the last two columns only that are required for our clustering analysis*

### K-Means Clustering

#### Determining number of Clusters
* We will find the WCSS(within cluster sum of squares) first using the formula below and then find the elbow   plot from it for 10 clusters.
```{r}
set.seed(6)
#wcss
wcss = vector()
for (i in 1:10) wcss[i] = sum(kmeans(customers, i)$withinss)
#Plot 10 clusters and their elbow
plot(1:10,
     wcss,
     type = 'b',
     main = paste('The Elbow Method'),
     xlab = 'Number of clusters',
     ylab = 'WCSS')
```


*K=5 clusters will be the right number of clusters to take as WCSS is not improving further after this point*

#### Building the Model
* We will build our model using `kmeans()` and specify the number of clusters required.
* All our 200 customers will be segmented to any of the 5 clusters using `kmeans()`.
```{r}
set.seed(29)
kmeans = kmeans(x = customers, centers = 5,iter.max = 300,nstart=10)
y_kmeans = kmeans$cluster
```

#### Visualising the clusters
* We will use the `clusplot()` to see our 5 clusters
```{r}
clusplot(customers,
         y_kmeans,
         lines = 0,
         shade = TRUE,
         color = TRUE,
         labels = 2,
         plotchar = FALSE,
         span = FALSE,
         main = paste('Clusters of customers'),
         xlab = 'Annual Income',
         ylab = 'Spending Score')
```


### Insights
* Customers characteristics in each clusters on the basis of cluster plot :
     + **cluster 1**-low income and low spending score(Sensible Customers)
     + **cluster 2** -average income and avg spending score(Standard Customers)
     + **cluster 3**-low income and High spending score(Careless Customers)
     + **cluster 4**- high income and low spending score(Careful Customers)
     + **cluster 5**- high income and high spending score(Target Customers)

